IOIs Analysis for Non-Expressive performances

### 2020-04-02 material/analysis/ioi.Rmd
exclude participant3
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

## Exclude outlier participants
```{r outlier, echo = FALSE}
excluded_ioi <- ioi[Mean < mean(ioi$Mean)+3*sd(ioi$SD) & Mean > mean(ioi$Mean)-3*sd(ioi$SD)]
print(excluded_ioi)
```

>>>>

## Exclude outlier participants
```{r outlier, echo = FALSE}
excluded_ioi <- ioi[Mean < mean(ioi$Mean)+3*mean(ioi$SD) & Mean > mean(ioi$Mean)-3*mean(ioi$SD)]
print(excluded_ioi)
```
